% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{TIANSHU TANG}

\basicInfo{
  \email{tstang@zju.edu.cn} \textperiodcentered\ 
  \phone{13588076479} }
 
\section{\faGraduationCap\  EDUCATION}
\datedsubsection{\textbf{Zhejiang University}, Zhejiang, China}{2020 -- Present}
\textit{Master Student}\ in Software Engineering, expected March, 2023
\datedsubsection{\textbf{Chongqing University of Posts and Telecommunications}, Chongqing, China}{2016 -- 2020}
\textit{B.S.}\ in Computer Science

\section{\faUsers\ EXPERIENCE}
\datedsubsection{Cloud platform for advance warning devices}{Mar. 2021 -- Present}
\role{JAVA Back-end Developer}{ZJU Binjiang Research Institute Cooperation Project}
Based on SpringBoot framework, we implemented the device protocol parsing module and cloud platform back-end data management module respectively. I led the project team to participate in Huawei Kunpeng Application Innovation Competition and won the second prize in Zhejiang Region Finals.
Personal work
\begin{itemize}
  \item Implemented device protocol parsing, and deployed MQTT server EMQX to maintain device connectivity
  \item Implemented real-time device online status query and dynamic delay of commands using redis
  \item Data management realized by Mysql, using Mybatis as the persistence layer framework
  \item Interface communication logging through AOP feature of Spring, and permission control enabled by both AOP and Custom Annotaion.
  \item Implemented user authorization using JWT
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ SKILLS}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java, Python, C
  \item Platform: Linux. Be familiar with common linux commands, and able to develop in linux environment, including writing shell scripts
  \item Data structure and Algorithms: Able to implement classical algorithms such as quick sort, merge sort, etc. Familiar with data structures such as linked list, skip list, binary search trees, etc.
  \item Web Framework: Understand the Spring Framework design concepts, such as IoC, AOP and other features, read some of the source code and understand its design patterns
  \item Database: Familiar with Mysql, experience in designing data tables, have knowledge of index optimization, SQL query optimization and underlying storage engine. Familiarity with Redis, and know the details of the underlying implementation principles of its basic data types
\end{itemize}

\section{\faHeartO\ HONORS AND AWARDS}
\datedline{\textit{Silver Medal}, Award on ACM-ICPC College Student Programming Competition Sichuan Region}{Apr. 2017}
\datedline{\textit{Grand Prize}, Award on National Student English Contest Finals}{Apr. 2017}
\datedline{\textit{\nth{2} Prize}, Award on Blue Bridge Cup National Software and Information Technology Professionals Competition National Finals}{Oct. 2018}
\datedline{\textit{\nth{2} Place}, Award on CCF Student Computer System and Programming Competition sub-region}{Apr. 2019}
\datedline{\textit{\nth{3} Prize}, Award on CCF Student Computer System and Programming Competition National Finals}{Oct. 2019}
\datedline{CCF National Outstanding Students}{Oct. 2019}
\datedline{National Scholarship}{Dec. 2019}

\section{\faInfo\ Miscellaneous}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item Language: English - Fluent(CET6 607), Mandarin - Native Speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}


